Accurate binding of calcium to phospholipid bilayers by effective inclusion of electronic polarization

### 2017-05-12 Manuscript/proto-manuscript.tex
Included some of Samuli's comments

Provides/predicts correct stoichiometry for \ce{Na^+}, \ce{Ca^{2+}} and their interaction energies with the lipid membrane.

@@

other lipids: charged lipid? -- ongoing research in our lab (starting to do something with Aniket on POPE for curved membranes)

>>>>

Provides/predicts correct stoichiometry for \ce{Na^+}, \ce{Ca^{2+}} and their interaction energies with the lipid membrane.
Samuli: the main selling argument would be that we solve the details (stoichiometry, coordination numbers, etc.) of cation binding in PC bilayer.

\textbf{Required figures}

Figure comparing order parameters and form factor between original Lipid14, new model and experiments,

- Figure showing order parameters as a function of \ce{NaCl} and \ce{CaCl_2} concentrations from Lipid14, new model and experiments (like current Fig. 1, but only original and final models)

- Figure(s) analysing binding details (density profiles, lipids bound per ion, something else?).

@@

other lipids: charged lipid? -- ongoing research in our lab (starting to do something with Aniket on POPE for curved membranes)
Samuli: From the point of view of this paper, the most relevant other lipid to study would be DPPC to see if we can reproduce the difference between POPC and DPPC in experiments.
